---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# citation

<!-- badges: start -->
<!-- badges: end -->

The goal of citation is to provide users an APA citation when given a user's Google API and article title. 

## Installation

You can install the development version of citation from [GitHub](https://github.com/) with:

```{r}
devtools::install_github("CindySun0309/citation")
```

## Attaining a Citation 

Given a Google API code and article title, the `APA()` function quickly retrieves the APA information of an article from Google Scholar.  

```{r example}
api_example <- readLines("example_api_k.txt")
library(citation)
example <- APA("Variation in Chinese population health related quality of life: results from a EuroQol study in Beijing, China", api_example)
example 
```


## Citation Data 
The metadata that comes with the citation package contains an example data frame which has one row, an article, and columns which associate with parts of the APA citation.  

```{r}
head(citation_data)
