---
title: "citation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{citation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(citation)
```

The `citation` package provides an R interface to retrieve APA citation about a research article (link the article) from Google scholar website - and most importantly, output a character string of the APA citation!

## Creating APA citations

Given a article title and the API code the `APA()` function  retrieves a JSON object with metadata about that APA format citation.

To utilize the `APA()` function, users must first generate an API key by signing up in advance [here](https://serpapi.com/users/sign_up). To create an account with [SerpAPI](https://serpapi.com/), users need to provide their email address and phone number during the registration process.
 
```{r}
API_key <- readLines("api.txt")
```

```{r example}
library(citation)

APA <- APA("Abuse is abuse: The influence of type of abuse, victim age, and defendant age on juror decision making", API_key)

APA
```

