---
title: "citation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{citation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
##library(citation)
```

The `citation` package provides an R interface to retrieve APA citation about a research article (link the article) from google scholar website - and most importantly, output a character string of the APA citation!

## Given the article title and the API code

Given a article title and the API code the `APA_citation()` function  retrieves a JSON object with metadata about that comic.

```{r example}
library(xkcd)

# Retrieve data about the first xkcd comic ever!
first_comic <- xkcd(1)
first_comic
```

The most useful thing you can do with these objects is plot them, which displays the comic image in your plot window.

```{r}
plot(first_comic)
```

## Comic Data
The metadata from all 2,850 xkcd comics (so far) is aggregated into the `xkcd_data` data set 

```{r}
head(xkcd_data)
```

What day of the week are xkcd comics published on most frequently?
```{r}
library(dplyr)
library(ggplot2)
```

```{r}
xkcd_data <- xkcd_data |> 
  mutate(date = as.Date(paste(year, month, day, sep = "/")),
         weekday = weekdays(date)
         )

xkcd_published <- xkcd_data |>
  count(weekday)
```

```{r}
ggplot(xkcd_published, aes(x = weekday, y = n)) +
  geom_col()
```

Saturday is for ~~the boys~~ xkcd!
